\subsection{Fulfilment of Initial Requirements}

In keeping with the principles of design science, it is important that the artifact described in section \ref{sec:design_iteration2} and demonstrated in section \ref{sec:demo} fulfils the requirements outlined in table \ref{table:requirements}. 

\paragraph{Lateral Coordination}

The first requirement is that the artifact supports the lateral coordination characteristic of a decentralized organization, and the decentralized authority structures and heterogeneous goals that go along with it. The three guidelines of the artifact -- being based on peer production -- inherently support lateral coordination over vertical coordination. The core characteristic of peer production is that a number of peers work together without a central coordinating authority (as it is in vertical coordination), which supports lateral coordination. The artifact supports decentralized authority structures and decision making (requirement 1.1) by suggesting that individual operational units are responsible for their own decision making. Furthermore, it suggests that the individuals in such a department make decisions collaboratively by giving each individual a vote for major decisions. This further supports heterogeneous goals (requirement 1.2) as each individual (and their respective views and goals) is able to contribute to making decisions.

\paragraph{Support of Governance Activities}

TOGAF and FEA make use compliance checking, standards and approval to ensure interoperability and integration of architecture artifacts. The proposed artifact instead suggests less formal style of governance which relies on individuals wilfully coordinating, an authority structure that gives them the freedom to act as they feel is best, and decisions that are made as peers rather than by management.

Being general guidelines, the specifics of how the artifact ensures interoperability and integration of EA components depends on the specific case. An example that fulfils the requirement of supporting governance activities is in the demonstration of the artifact. Here it is proposed that the governance of systems (and therefore the EA artifacts that they result from) is accomplished by collaboratively classifying them as either essential and non-essential. The specific guidelines for interoperability are different for the two classifications. This is a style of governance that follows the guidelines of wilful coordination, decentralized authority structure and peer decision making: individual business units come together to decide on the classification of essential systems, and the implementation of non-essential systems is completely up to discretion of the individual business units. 

%Requirement 2? --> wilful coordination + voting for approval?
%
%%TODO reflect decisions in design "peer decision making"
%%TODO maybe also suggest discussion groups/meetings instead of just voting
%%TODO fix requirements table
%
%Goals -> everyone has a voice
%
%demonstrated in section \ref{sec:demo} addresses this requirement by proposing six changes to the coordination practices of the case organization. The first suggestion addresses how 
%  
%The   model  shall  support  lateral coordination
%1.1 The model shall support decentralized authority structures  --> peer produced strategy
%1.2 The model shall support heterogeneous goals
%
%The model shall support governance activities --> IT does this
%2.1 The model shall address architecture interoperability and integration issues
%2.2 The model shall support approving architectural artifacts for implementation
%2.3 The model shall support accountability


\subsection{Advantages of the Proposed Peer Production Governance Framework}

%In order for the artifact to be beneficial for the case organization, it needs to provide some benefits over their current implicit EA and over a more traditional, centralized form of governance. 

In order for the artifact to be considered valid, its demonstration needs to offer benefits over the case's as-is architecture and traditional EA suggestions. This demonstration was done by outlining the as-is governance framework of the case, a proposed peer production based framework, as well as an example of how their framework could work in a centralized manner. Consequently, this section will discuss the three frameworks that make up the artifact's demonstration and how the peer production framework can offer an advantage over the other two. 

%TODO word that better

The peer production based framework differs from the as-is and centralized governance frameworks in a number of facets. In terms of decision rights allocation, the peer production based framework keeps the same operating principle as the as-is framework -- to push decision making as far down to the operational level as possible -- whereas a centralized framework would instead keep decision making in the upper levels of management. As most of the staff are operationally-focused (e.g. professors, researchers, and PhDs), this would likely be a sub-optimal situation. 

Budgeting in both the as-is and centralized frameworks is centralized, which is in conflict with the decentralized IT management. In the peer production based framework, a mix between  centralized and decentralized is instead proposed. Here, the budget is still allocated centrally, however the department then has complete control over their allocated amount. This could potentially remove the conflict as the department would then have the necessary control over their own budget to operate in a manner decentralized from the rest of the organization. 

The setting of strategy and overall operating principles for the department is centralized in both the centralized and as-is frameworks. In the peer production framework, a mixed style of governance has been proposed in its place. The decentralized component is that the department members produce the operating principles and strategy using peer production while the centralized component is that approval is still needed from the faculty. This offers the advantage of allowing the department to set a strategy that reflects all aspects of the department (by having input from everyone instead of just the department board) that is still compatible with the rest of the university (as approval is needed by the faculty).

%Decision rights
% C --> A minimum of decision rights are pushed down to the operational level.
% D --> same as as-is

%Budgeting 
% C --> same as as-is
% D --> remove that ability of the central to make decisions for the dept

%%%%Advisory group
%%%% C --> made up of upper management
%%%% D --> same

%Strategy and vision
% C --> same
% D --> members control over setting

The suggested peer production framework is significantly different from the as-is and centralized frameworks. It seeks to maintain the departmental-independence prevalent in the as-is framework while addressing the incompatible architecture components this results in. This is primarily accomplished through the cooperative classification of essential and non-essential systems, and the difference in governance for the two types. This classification is done in a collaborative manner by the departments, for example by giving each department a vote. Systems classified as essential are required to be used or integrated with by the departments while departments have the option to choose if they want to utilize systems classified as non-essential. These changes are addressed at reconciling differences between the two architecture principles identified previously identified without actually changing the principles. Decision rights are still pushed down and systems are still integrated throughout the organization, but this change in governance addresses the conflict that can arise when a decision is made to implement a decentralized system that the rest of the organization is integrating (as it stands in the as-is framework). In comparison, shifting to centralized governance (as in the centralized governance framework) would require changing the principle of pushing decision-making down to the operational level. As this is a core principle of the organization, this change would have a significant impact across the entire organization, with no guarantee of it being a positive one. 

%With completely centralized IT, the department IT would be a subordinate entity to the central IT (or even not exist at all). 
%
%IT 
%
%Move to completely centralized IT
%
%IT Approval
% C --> decided on by university IT
% D --> projects run by IT, approval granted collab (instead of from above)
%
%Essential Systems 
% C --> same as as-is
% D --> Departments determine what is essential collaboratively. All departments pay for and use these systems.
%
%Non-essential
% C --> decision made by the university
% D --> Opt-in (only pay for opting in)
%

\subsection{Limitations of the Case}

There are two main limitations of the case which are the main limitations of the thesis: The first is a lack of explicit EA and the second is that the artifact was not able to be formally evaluated. These limitations are primarily due to the difficulty in finding a case organization that is both decentralized and implements some style of explicit EA. 

The EA of the case is implicit rather than explicit, i.e. they do not implement an accepted EA framework but they do organize their activities in some manner; this is their 'implicit EA'. As an implicit EA does not explicitly make use of the concepts EA frameworks, it becomes difficult to draw parallels -- which are very open to interpretation -- between the case's EA and the EA frameworks of TOGAF, Zachman, and FEA. Furthermore, the validity of the interpretations, and thus the results, may be somewhat negatively affected by this. 

The second main limitation of the thesis is that there was no opportunity to apply the presented artifact in practice, thus preventing a formal evaluation of the artifact. The demonstration shows that the artifact is plausible, however the lack of an evaluation makes it difficult to say for certain if the artifact solves the problems identified in section \ref{sec:exproblem}.

Despite these limitations, the findings of this thesis are still interesting as this thesis is part of a research work in its early phases, and as such is exploratory in nature. The ideas presented here have been used to form the basis for two papers that were accepted in two conferences, PoEM\footnote{\url{http://poem2013.rtu.lv}} 2013 and the TEAR workshop at IEEE EDOC\footnote{\url{http://planet-sl.org/edoc2013/}} 2013: \cite{speckert2013} and \cite{rychkova2013}.

  